FantasticLamp: a genome graph based pipeline for calculating the efficacy of genomic edits

### 2023-07-09 paper/main.tex
Edited small details

Casper~Schutte\,$^{\orcidlink{0000-0003-4245-6842}\text{\sfb 1}}$,
Erik~Garrison\,$^{\orcidlink{0000-0003-3821-631X}\text{\sfb 2}*}$,
Ian~T~Fiddes\,$^{\orcidlink{0000-0002-1580-7443}\text{\sfb 3}}$

}

\address{
$^{\text{\sf 1}}$Department of Bioinformatics and Computational Biology, University of Stellenbosch, Stellenbosch, 7600, Western Cape, South Africa \\
$^{\text{\sf 2}}$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, 38163, Tennessee, USA \\
$^{\text{\sf 3}}$Ian's affiliation goes here \\
%
}

>>>>

Casper~Schutte\,$^{\orcidlink{0000-0003-4245-6842}\text{\sfb 1}}$,
Ian~T~Fiddes\,$^{\orcidlink{0000-0002-1580-7443}\text{\sfb 2}}$,
Erik~Garrison\,$^{\orcidlink{0000-0003-3821-631X}\text{\sfb 3}*}$
}

\address{
$^{\text{\sf 1}}$Department of Bioinformatics and Computational Biology, University of Stellenbosch, Stellenbosch, 7600, Western Cape, South Africa \\
$^{\text{\sf 2}}$Ian's affiliation goes here \\
$^{\text{\sf 3}}$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, 38163, Tennessee, USA \\
}
